TGI Spinal Analysis Code

### 2022-12-15 analysis/tgi-spinal_analysis.Rmd
adding non zero plots and finalising analysis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Loading libraries
# check for pacman package and install if not found
if (!require("pacman")) install.packages("pacman")
  pacman::p_load(boot, broom, broom.mixed, brms, caret, corrplot, DHARMa, gamlss,
                 gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
                 modelsummary, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
                 rsample, rstatix, simr, tibble, tidyverse, wesanderson
                 )
```

@@

Hypothesis 2 a & b: relative location of warm and cold
```{r h2}
# Summary statistics
# First, change name of manipulation
vas_meds$manipulation <- factor(vas_meds$manipulation, labels = c('Non-TGI', 'TGI'))
h2_sum <- summarySEwithin(data = vas_meds, measurevar = 'VAS', 
                          withinvars = c('quality','manipulation','cold_probe'))

@@

# plot all data - half-violins
# COLD
ggplot(data = vas_meds %>% 
         filter(quality == 'cold'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum %>% 
               filter(quality == 'cold'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum %>% 
               filter(quality == 'cold'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum %>% 
              filter(quality == 'cold'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(blue[4], blue[6])) +
  scale_fill_manual(values = c(blue[4], blue[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Cold ratings', x = NULL, 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_cold_plot

@@

ggsave('h2_alldat_plot.png', h2_plot, device = NULL, path = anaPath,
       width = 10, height = 6.5, dpi = 600)
```
# Plot 32 burn responders seperately
```{r burn32}
```

@@

# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
df_long$VAS <- df_long$VAS/100
df_long$ID <- factor(df_long$ID)
```

@@

model.cold1 = gamlss(VAS ~ manipulation * condition * cold_cond + procedure + trial_n +
                                random(ID),
                    nu.formula = ~ 1+manipulation,
                    tau.formula = ~ 1+manipulation,
                    family = BEINF(mu.link = 'logit', sigma.link = 'logit', nu.link = 'logit', 
                                   tau.link = 'logit'),
                    data = test %>% filter(quality == 'cold'),
                    trace = F) 
mc1 <- summary(model.cold1)
mc1
```
# Warm
```{r warmmod}
# Try and model all with ratings
model.warm = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond +
                                trial_n + (1|ID) + (1|order),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_long %>% filter(quality == 'warm'),
                      na.action = na.omit) 
mw <- summary(model.warm)
mw
```

@@

@@

# Run model checks on all
```{r checks, warning=FALSE}
# cold assumption - on n = 50
mc.assump <- simulateResiduals(model.cold, n = 1000)
plot(mc.assump)
# warm assumption - on n = 50
mw.assump <- simulateResiduals(model.warm, n = 1000)
plot(mw.assump)
# warm assumption - on n = 50
mb.assump <- simulateResiduals(model.burn, n = 1000)
plot(mb.assump)
```
# Run individual models on within and across dermatomes for H2
Directly compare proximal-distal and rostral-caudal results for each quality

# EXPLORATORY HYPOTHESES
# Correlation between quality (cold/warm/burn)

@@

# correlation matrix
# plotting correlations between variables
corrplot(cormat, type = 'lower',
         p.mat = p, insig = "p-value", sig.level = -1,
         title = "VAS rating correlation matrix", 
         mar = c(0,0,1,0), 
         tl.cex=0.9) 
```
# Scatter plots
```{r scatter}
# Non TGI plots
ggplot(df_corr, aes(x = CNTcold, y =CNTwarm)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[1,3], 2))),
            x=8, y=90, size = 5) +
  labs(x = 'Cold Ratings', y = 'Warm Ratings') +
  xlim(0,100) + ylim(-15,100) +
  theme_bw() -> CNT_cw_plot

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Loading libraries
# check for pacman package and install if not found
if (!require("pacman")) install.packages("pacman")
  pacman::p_load(boot, broom, broom.mixed, brms, car, caret, corrplot, DHARMa, gamlss,
                 gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
                 modelsummary, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
                 rsample, rstatix, simr, tibble, tidyverse, wesanderson
                 )
```

@@

Hypothesis 2 a & b: relative location of warm and cold
```{r h2}
# Change name of manipulation
vas_meds$manipulation <- factor(vas_meds$manipulation, labels = c('Non-TGI', 'TGI'))
h2_sum <- summarySEwithin(data = vas_meds, measurevar = 'VAS', 
                          withinvars = c('quality','manipulation','cold_probe'))

@@

# plot all data - half-violins
# COLD
ggplot(data = vas_meds %>% 
         filter(quality == 'cold'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'proximal')) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'distal')) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'caudal')) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'rostral')) +
  facet_wrap(~manipulation)

  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum %>% 
               filter(quality == 'cold'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum %>% 
               filter(quality == 'cold'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum %>% 
              filter(quality == 'cold'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(blue[4], blue[6])) +
  scale_fill_manual(values = c(blue[4], blue[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Cold ratings', x = NULL, 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_cold_plot

@@

ggsave('h2_alldat_plot.png', h2_plot, device = NULL, path = anaPath,
       width = 10, height = 6.5, dpi = 600)
```

# Same plot, no zeros
```{r h2nozero}
# First, remove zeros from trials to better represent analysis
vas_nozero <- all_vas %>% 
  filter(VAS > 0)

vas_meds1 <- aggregate(VAS ~ quality*manipulation*condition*cold_probe*ID, 
                      median, data = vas_nozero)

# Change name of manipulation
vas_meds1$manipulation <- factor(vas_meds1$manipulation, labels = c('Non-TGI', 'TGI'))
h2_sum1 <- summarySEwithin(data = vas_meds1, measurevar = 'VAS', 
                          withinvars = c('quality','manipulation','cold_probe'))

# organise data for plotting
vas_meds1$cold_probe <- factor(vas_meds1$cold_probe, levels = 
                                c('proximal', 'distal', 'rostral', 'caudal'))
h2_sum1$cold_probe <- factor(h2_sum1$cold_probe, levels = 
                                c('proximal', 'distal', 'rostral', 'caudal'))
# recoding cold probe location so can jitter
vas_meds1$cold_code <- factor(vas_meds1$cold_probe, labels = 
                                c(1,2,3,4))
h2_sum1$cold_code <- factor(h2_sum1$cold_probe, labels = 
                                c(1,2,3,4))
# creating jitter
vas_meds1$xj <- jitter(as.numeric(vas_meds1$cold_code), amount = .05)

# plot all data - half-violins
# COLD
ggplot(data = vas_meds1 %>% 
         filter(quality == 'cold'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum1 %>% 
               filter(quality == 'cold'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum1 %>% 
               filter(quality == 'cold'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum1 %>% 
              filter(quality == 'cold'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(blue[4], blue[6])) +
  scale_fill_manual(values = c(blue[4], blue[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Cold ratings', x = NULL, 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_cold_plot

# WARM
ggplot(data = vas_meds1 %>% 
         filter(quality == 'warm'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum1 %>% 
               filter(quality == 'warm'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum1 %>% 
               filter(quality == 'warm'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum1 %>% 
              filter(quality == 'warm'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(oran[4], oran[6])) +
  scale_fill_manual(values = c(oran[4], oran[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Warm ratings', x = 'Location of cold probe', 
         y = NULL) +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_warm_plot

# BURN
ggplot(data = vas_meds1 %>% 
         filter(quality == 'burn'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'burn', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'burn', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'burn', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum1 %>% 
               filter(quality == 'burn'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum1 %>% 
               filter(quality == 'burn'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum1 %>% 
              filter(quality == 'burn'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(purp[4], purp[6])) +
  scale_fill_manual(values = c(purp[4], purp[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Burn ratings', x = 'Location of cold probe', 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_burn_plot

# arrange entire plot
h21_plot <- ggarrange(h2_cold_plot, h2_warm_plot, h2_burn_plot,
                     nrow = 2, ncol = 2)
h21_plot

ggsave('h2_nozero_plot.png', h21_plot, device = NULL, path = anaPath,
       width = 10, height = 6.5, dpi = 600)
```

# Differences
```{r h2diff}
# recode cold_location and condition to reduce levels in regression
vas_meds$cold_cond[vas_meds$cold_probe == 'distal'] <- 'dist_rost' 
vas_meds$cold_cond[vas_meds$cold_probe == 'rostral'] <- 'dist_rost' 
vas_meds$cold_cond[vas_meds$cold_probe == 'proximal'] <- 'prox_caud' 
vas_meds$cold_cond[vas_meds$cold_probe == 'caudal'] <- 'prox_caud'

# then pivot wider and calculate difference
vas_h2_diff <- vas_meds %>% 
  select(-c(cold_code, xj, cold_probe)) %>% 
  pivot_wider(id_cols = c(ID, quality, manipulation, condition), 
              names_from = cold_cond, values_from = VAS) %>% 
  mutate(difference = prox_caud - dist_rost)
# recode quality
vas_h2_diff$quality <- factor(vas_h2_diff$quality,
                           levels = c('cold', 'warm', 'burn'))
# summary statistics
h2_diff_sum <- summarySEwithin(data = vas_h2_diff, measurevar = 'difference',
                               withinvars = c('manipulation', 'quality', 'condition'))

# plot the differences - within
ggplot(data = vas_h2_diff %>% 
         filter(condition == 'within'), 
       aes(manipulation, difference, colour = quality)) +
  geom_hline(yintercept = 0) +
  geom_point(aes(group = ID), position = position_dodge(.2), alpha = .5) +
  geom_point(data = h2_diff_sum %>% 
               filter(condition == 'within'), 
             aes(manipulation, difference), colour = 'grey15',
             fill = 'grey15',
             shape = 21, size = 3) +
  geom_errorbar(data = h2_diff_sum %>% 
               filter(condition == 'within'), 
               aes(manipulation, ymin = difference-ci, ymax = difference+ci),
               width = .1, size = .7, colour = 'grey15') +
  scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
  labs(title = 'Hypothesis 2 Cold & Warm Afferents: Within',
       y = 'Proximal - Distal VAS Ratings', x = NULL) +
  facet_wrap(~quality) +
  theme_classic()

# plot the differences - across
ggplot(data = vas_h2_diff %>% 
         filter(condition == 'across'), 
       aes(manipulation, difference, colour = quality)) +
  geom_hline(yintercept = 0) +
  geom_point(aes(group = ID), position = position_dodge(.2), alpha = .5) +
  geom_point(data = h2_diff_sum %>% 
               filter(condition == 'across'), 
             aes(manipulation, difference), colour = 'grey15',
             fill = 'grey15',
             shape = 21, size = 3) +
  geom_errorbar(data = h2_diff_sum %>% 
               filter(condition == 'across'), 
               aes(manipulation, ymin = difference-ci, ymax = difference+ci),
               width = .1, size = .7, colour = 'grey15') +
  scale_colour_manual(values = c(blue[5], oran[5], purp[5])) +
  labs(title = 'Hypothesis 2 Cold & Warm Afferents: Across',
       y = 'Caudal - Rostral VAS Ratings', x = NULL) +
  facet_wrap(~quality) +
  theme_classic()
```

# Plot 32 burn responders seperately
```{r burn32}
```

@@

# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
#df_long$VAS <- df_long$VAS/100
df_long$ID <- factor(df_long$ID)
```

@@

Anova(model.cold)

model.cold1 = gamlss(VAS ~ manipulation * condition * cold_cond + procedure + trial_n +
                                random(ID),
                    nu.formula = ~ 1+manipulation,
                    tau.formula = ~ 1+manipulation,
                    family = BEINF(mu.link = 'logit', sigma.link = 'logit', nu.link = 'logit', 
                                   tau.link = 'logit'),
                    data = test %>% filter(quality == 'cold'),
                    trace = F) 
mc1 <- summary(model.cold1)
mc1
```
# Warm
```{r warmmod}
# Try and model all with ratings
model.warm = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond +
                                trial_n + (1|ID) + (1|order),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_long %>% filter(quality == 'warm'),
                      na.action = na.omit) 
mw <- summary(model.warm)
mw

Anova(model.warm)
```

@@

Anova(model.burn)

@@

# Run model checks on all
```{r checks, warning=FALSE}
# cold assumption - on n = 50
mc.assump <- simulateResiduals(model.cold, n = 1000)
plot(mc.assump)
# warm assumption - on n = 50
mw.assump <- simulateResiduals(model.warm, n = 1000)
plot(mw.assump)
# warm assumption - on n = 50
mb.assump <- simulateResiduals(model.burn, n = 1000)
plot(mb.assump)
```
# EXPLORATORY HYPOTHESES
# Correlation between quality (cold/warm/burn)

@@

# correlation matrix
# plotting correlations between variables
corrplot(cormat, type = 'lower',
         p.mat = p, insig = "p-value", sig.level = -1,
         title = "VAS rating correlation matrix", 
         mar = c(0,0,1,0), 
         tl.cex=0.9) 
```

# Scatter plots
```{r scatter}
# Non TGI plots
ggplot(df_corr, aes(x = CNTcold, y =CNTwarm)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  geom_text(aes(label = paste0("R = ",
                               round(cormat[1,3], 2))),
            x=8, y=90, size = 5) +
  labs(x = 'Cold Ratings', y = 'Warm Ratings') +
  xlim(0,100) + ylim(-15,100) +
  theme_bw() -> CNT_cw_plot

@@

# Run individual models on within and across dermatomes for H2
Directly compare proximal-distal and rostral-caudal results for each quality
